External Patch Group Prior Guided Internal Orthogonal Dictionary Learning for Real Image Denoising

### 2016-10-23 CVPR2017_Review_Unified.tex
aa

\section{Related Work}
\subsection{Patch Group Prior of Natural Images}
The Patch Group (PG) prior \cite{pgpd} is proposed to directly model the non-local self similar (NSS) property of natural images. The NSS property is commonly used in image restoration tasks \cite{nlm,bm3d,lssc,wnnm,pgpd}. The PG prior largely reduces the space of images to be modeled when compared to the patch prior \cite{epll}. The better modeling on NSS is demonstrated via better image denoising performance on natural images. However, in \cite{pgpd}, only the PGs of clean natural images is utilized, while the PGs of noisy input images are ignored. In this paper, we aim at making use of both PGs from natural clean images and real noisy images for better denoising performance.

>>>>

\section{Related Work}
\subsection{Patch Group Prior of Natural Images}
The Patch Group (PG) prior \cite{pgpd} is proposed to directly model the non-local self similar (NSS) property of natural images. The NSS property is commonly used in image restoration tasks \cite{nlm,bm3d,lssc,wnnm,pgpd}. The PG prior largely reduces the space of images to be modeled when compared to the patch prior \cite{epll}. In \cite{pgpd}, only the PGs of clean natural images is utilized, while the PGs of noisy input images are ignored. In this paper, we make use of PGs both from external clean images and internal given real noisy image for better denoising performance.
